Supplemental Methods: No robust coexistence in a canonical model of plant-soil feedbacks

### 2021-10-27 paper/supp_methods.tex
added text explaining simulations

\begin{align} \label{derive_relative}
\begin{split}
	\frac{dp_i}{dt} &= \frac{d}{dt} \frac{x_i}{\sum x_j}\\  
	&= \frac{1}{\sum_j x_j} \frac{dx_i}{dt} - \frac{x_i}{(\sum_j x_j)^2} \sum_j \frac{dx_j}{dt} \\
	&= \frac{x_i}{\sum_j x_j} \left( \sum_{j} \alpha_{ij} \, q_j \right) - \frac{x_i}{\sum_j x_j} \left(\sum_j \frac{x_j}{\sum_k x_k} \sum_{l} \alpha_{jl} \, q_l \right)\\
	&= p_i \left(\sum_{j} \alpha_{ij} \, q_j -  \sum_{j, k} \alpha_{jk} p_j  q_k \right) \, .
\end{split}
\end{align}
This last expression is identical to the first line of Eq.~5 in the Main Text. The dynamics for $q_i$ can be derived in exactly the same way (using the definitions $\beta_{ii} = \beta_i$ and $\beta_{ij} = 0$). The two terms of each per capita growth rate in Eq.~5 have natural interpretations in the language and notation of linear algebra: $\sum_{j} \alpha_{ij} \, q_j$ is the $i$th component of the matrix-vector product $A \bm{q}$ and $\sum_{j, k} \alpha_{jk} p_j  q_k$ is the bilinear form $\bm{p}^T A \bm{q}$. Here, $A$ (and $B$) is an $n \times n$ matrix and $\bm{p}$ ($\bm{q}$) is a vector of length $n$, as described in the Main Text. We can re-write Eq.~5 as
\begin{align}
\begin{split}
	\frac{dp_i}{dt} &= p_i \left((A \bm{q})_i - \bm{p}^T A \bm{q} \right) \\
	\frac{dq_i}{dt} &= q_i \left((B \bm{p})_i - \bm{q}^T B \bm{p} \right) \\
\end{split}
\end{align}
or even more compactly as
\begin{align}
\begin{cases}
\frac{d\bm{p}}{dt} &= D(\bm{p}) \left(A \bm{q} - (\bm{p}^T A \bm{q}) \bm{1} \right) \\
\frac{d\bm{q}}{dt} &= D(\bm{q}) \left(B \bm{p} - (\bm{q}^T B \bm{p}) \bm{1}  \right) \,
\end{cases}
\end{align}
which is Eq.~6 in the Main Text.

@@

>>>>

\begin{align} \label{derive_relative}
\begin{split}
	\frac{dp_i}{dt} &= \frac{d}{dt} \frac{x_i}{\sum x_j}\\  
	&= \frac{1}{\sum_j x_j} \frac{dx_i}{dt} - \frac{x_i}{(\sum_j x_j)^2} \sum_j \frac{dx_j}{dt} \\
	&= \frac{x_i}{\sum_j x_j} \left( \sum_{j} \alpha_{ij} \, q_j \right) - \frac{x_i}{\sum_j x_j} \left(\sum_j \frac{x_j}{\sum_k x_k} \sum_{l} \alpha_{jl} \, q_l \right)\\
	&= p_i \left(\sum_{j} \alpha_{ij} \, q_j -  \sum_{j, k} \alpha_{jk} p_j  q_k \right) \, .
\end{split}
\end{align}
This last expression is identical to the first line of Eq.~5 in the Main Text. The dynamics for $q_i$ can be derived in exactly the same way (using the definitions $\beta_{ii} = \beta_i$ and $\beta_{ij} = 0$). The two terms of each per capita growth rate in Eq.~5 have natural interpretations in the language and notation of linear algebra: $\sum_{j} \alpha_{ij} \, q_j$ is the $i$th component of the matrix-vector product $A \bm{q}$ and $\sum_{j, k} \alpha_{jk} p_j  q_k$ is the bilinear form $\bm{p}^T A \bm{q}$. Here, $A$ (and $B$) is an $n \times n$ matrix and $\bm{p}$ ($\bm{q}$) is a vector of length $n$, as described in the Main Text. We can re-write Eq.~5 as
\begin{align}
\begin{split}
	\frac{dp_i}{dt} &= p_i \left((A \bm{q})_i - \bm{p}^T A \bm{q} \right) \\
	\frac{dq_i}{dt} &= q_i \left((B \bm{p})_i - \bm{q}^T B \bm{p} \right) \\
\end{split}
\end{align}
or even more compactly as
\begin{align}\label{compact_form}
\begin{cases}
\frac{d\bm{p}}{dt} &= D(\bm{p}) \left(A \bm{q} - (\bm{p}^T A \bm{q}) \bm{1} \right) \\
\frac{d\bm{q}}{dt} &= D(\bm{q}) \left(B \bm{p} - (\bm{q}^T B \bm{p}) \bm{1}  \right) \,
\end{cases}
\end{align}
which is Eq.~6 in the Main Text.

@@

\section{Numerical Simulations}
In order to offer numerical evidence that complements our analytical findings, we  integrate  Eq.~\ref{compact_form} with 2, 3, 5, and 6 initial plant species and soil communities. For each case, we perform 5000 numerical integrations sampling the payoff matrices at random each time. At each integration we (1) sample non-singular payoff matrices $ A $ and $ B $ from the uniform distribution U(0, 1), and (2) integrate the system until an equilibrium with $\leq 2$ species is reached.
